\section{Evaluation of cloud criteria}\label{sec:ch4}
As defined by the US-based \textit{National Institute of Standards and Technology}
(NIST) a cloud service must fulfill certain criteria \cite{nistCloud}. This 
section gives a brief overview and reviews the application's fulfillment of each.
\begin{itemize}
    \item \textbf{On-Demand Self Service:} Users can create and scale resources 
    through the aforementioned (chapter \ref{sec:ch2}) user interfaces at any time
    and to any capacity they desire. Only starting up and allocating resources 
    takes some time. The implementation uses the Azure API to do so.
    \item \textbf{Broad Network Access:} Provided, as Microsoft holds a global 
    server network and content can be delivered as HTML to be viewed in browsers 
    on supporting devices. The access can be expanded by using the CDN component 
    proposed in chapter \ref{sec:ch2}.
    \item \textbf{Resource Pooling:} Resources can be organized in logical groups,
    but that's not the point: Resources of the provider are shared between 
    multiple users, called 'tenants'. This is a given as it is not clear where exactly
    100 GB of videos are saved, aside from a geographical region. Most likely it is also
    just a partition on a bigger server hard disk instead of a dedicated device.
    \item \textbf{Rapid Elasticity:} Illusion of infinite resources and scaling: 
    provided by Azure as long as end users have a valid subscription and the cost 
    plan includes scaling. Vertical scaling (scale-up) requires manual action, 
    especially because the shift in price between tiers can be dramatic. 
    Horizontal scaling (scale-out) also depends in some cases from price tiers. 
    Scale-outs usually depend on parameter like CPU, RAM or storage usage (in case of the NodeJS 
    webservice). Other services scale totally automatic, as the payment is per GB used per month
    (BlobStorage, Streaming Throughput).
    \item \textbf{Measured Services:} Provided by Azure: the Insights and Billing modules
    offer in-depth statistics and analysis of resource usage and generated costs. It's even
    possible to configure Alerts, such as automatic sending of E-Mails or SMS for specific events,
    such as reaching a set cost for the current month or should autoscaling be triggered. Moreover, the implementation specific measurement will be the time that a 
    user spends watching videos and storage that is used by one user.
\end{itemize}
