% Tabelle mit der Kostenaufstellung von Azure, skalierbare Elemente
% in versch. Tiern, also am Anfang nur 100GB BlobStorage, später 1TB, dann 10TB
% Kosten am Anfang (Tier 1): ca. 40 Euro im Monat, also mit einem Hartz4-Satz fast ein Jahr lang bezahlbar
% Das teuerste ist anfangs der AppService
% Finanzierung wird erst ein Problem, wenn viel mehr Content und Traffic anfallen
Using CDN is preferable, because ``When Azure CDN is not enabled for Media Services, data transfer is charged at Data Transfer Pricing. When Azure CDN is enabled for Streaming Units, data transfer charges do not apply. Data transferred is instead just charged at standard CDN pricing.'' 
% https://azure.microsoft.com/en-us/pricing/details/cdn/   vs   https://azure.microsoft.com/en-us/pricing/details/bandwidth/
While at first the pricing for both is near identical, it's the range from the 50th on to the 150th TB in one month that already shows the disparity: \$0.07 per GB through standard file transfer vs  \$0.0037 via CDN.
Bandwidth and CDN are also priced differently depending on region

According to an online filesize calculator \footnote{\url{https://toolstud.io/video/filesize.php}} a 25 FPS FullHD-Video of 20 minutes length would estimate to around 1 GB in size (average between \textit{YoutubeHD} and \textit{NetflixHD} with a necessary bandwidth of 8Mbps (1MB/s) in case of \textit{YoutubeHD} bitrate.  % ?imagewidth=1920&imageheight=1080&framerate=25&timeduration=60&timeunit=minutes
Assume that after a good start there are now 100 videos as the one described before. A total of 500 visitors arrive each month and watch 2 videos each: $(500 \ast 2 GB) = 1TB$ Streaming Throughput and $(500 \ast 2 \ast 20 min)  = 2000$ minutes (33,33 hours) of streamed video. (1000GB * 0,08ct) = 80 dolurs
The necessary blob storage amounts to $100 \ast 1GB = 100GB$. 
Let's also assume we receive 10 new videos each month, which results in an encoding output of $(10 \ast 20 mins) = 200$ minutes (6.75 dolurs).  

This brings us to a rough estimate (appsrv+streaming + encoding + storage) of 130 dolls each month. Spreading the costs to the users means every user uses services worth (130 / 500) = 0,26ct. If we omit the costs for the AppService and only account for costs generated through user interaction we get (90 / 500) = 0,18ct per user. The AppService is a mostly fixed cost as it is billed per running time, but media services costs scale upwards with user interaction.

Kosten: 80/20 Creator / SciTube
Every encoding costs: $Length * BasePriceHD$
Every view costs: $VideoSize * (Streaming+CDN)$
Every vid costs: $Size * StoragePrice$
Every month costs: $AppServiceBasePrice * Throughput$
